---
title: "Quant Finance (Streaming Services Portfolio)"
output: html_document
---

## Acquiring Data
Acquiring data from Yahoo Finance of AAPL, NFLX, ROKU, SPOT, DIS equities
```{r}
library(plotly)
library(ggplot2)
library(quantmod)
library(PerformanceAnalytics)
library(dplyr)

#starting data
dt<-'2018-2-1'
#getting data
aapl_df<-data.frame(getSymbols.yahoo('AAPL', from=dt, auto.assign=F))
nflx_df<-data.frame(getSymbols.yahoo('NFLX', from=dt, auto.assign=F))
roku_df<-data.frame(getSymbols.yahoo('ROKU', from=dt, auto.assign=F))
spot_df<-data.frame(getSymbols.yahoo('SPOT', from=dt, auto.assign=F))
dis_df<-data.frame(getSymbols.yahoo('DIS', from=dt, auto.assign=F))
```
## Data Overview
Looking at SPOT equity data as an example 
```{r}
spot_table<-head(spot_df,10)
spot_table
```
## Data Preparation
Manipulating raw equity data for future analysis
```{r}

data_prep_func<-function(x, y){
  #sma
  sma10<-SMA(x[6], n=10)
  #ema
  ema20<-EMA(x[6], n=20)
  #BBands
  bbands20 <- data.frame(BBands( Cl(x), n=20, sd=2))
  bbands20 <- bbands20[,c(1,3)]
  #changing colnames
  colnames(sma10)<-c(paste0(y,'.SMA'))
  colnames(ema20)<-c(paste0(y,'.EMA'))
  colnames(bbands20)<-c(paste0(y,'.dn'), paste0(y,'.up'))
  #merge/formatting
  new_df<-x
  new_df<-cbind(new_df, sma10)
  new_df<-cbind(new_df, ema20)
  new_df<-cbind(new_df, bbands20)
  new_df<-cbind(Date=rownames(new_df), new_df)
  rownames(new_df)<-1:nrow(new_df)
  #volume differentiation calc
  for(v in 1:length(new_df[,1])){
    if(new_df[v, 5] >= new_df[v, 2]){
      new_df[v, 'volumetype']='Increasing'
    } else if(abs(new_df[v, 5]-new_df[v,2]) < 0.4){
      new_df[v, 'volumetype']='Doji'
    } else {
      new_df[v, 'volumetype']='Decreasing'
    }
  }
  #return
  return(new_df)
}
#running func
aapl_df<-data_prep_func(aapl_df, 'AAPL')
dis_df<-data_prep_func(dis_df, 'DIS')
nflx_df<-data_prep_func(nflx_df, 'NFLX')
roku_df<-data_prep_func(roku_df, 'ROKU')
spot_df<-data_prep_func(spot_df, 'SPOT')
```
## Data Visualization
Creating a dynamic plot with Plotly lib
```{r}
data_viz1_func<-function(df, eq_name){
  #starting data
  dt<-'2018-2-1'
  #today's date
  today_date<-Sys.Date()
  #plot
  candle_fig <- plot_ly(x = df[[1]], type="candlestick",
                      open = df[[2]], close = df[[5]],
                      high = df[[3]], low = df[[4]], name=eq_name,
                      width=900, height=800)
  candle_fig <- candle_fig %>% add_lines(x = df[[1]], y = df[[8]],
                                       line = list(color = 'rgb(255, 153, 102)',
                                                   width = 0.8),
                                       name='SMA-10', inherit = F)
  candle_fig <- candle_fig %>% add_lines(x = df[[1]], y = df[[9]],
                                       line = list(color='blue',
                                                   width=0.8),
                                       name='EMA-20', inherit = F)
  candle_fig <- candle_fig %>% add_lines(x = df[[1]], y = df[[10]],
                                       line = list(color='#dad3e0',
                                                   width=0.8,
                                                   opacity=0.6),
                                       name='BBands.dn', inherit = F)
  candle_fig <- candle_fig %>% add_lines(x = df[[1]], y = df[[11]],
                                       line = list(color='#dad3e0',
                                                   width=0.8,
                                                   opacity=0.6),
                                       name='BBAnds.up', inherit = F)
  volume_fig <- aapl_df %>% plot_ly(x= df[[1]], y= df[[6]],
                                  type='bar', name = df[[12]],
                                  color= df[[12]],
                                  colors=c('#ff9999',
                                           '#ffff99',
                                           '#99ffb3')
                                  )
  #layout
  volume_fig <- volume_fig %>% layout(yaxis=list(title='Volume',
                                               titlefont=list(size=15)))
  final_fig <- subplot(candle_fig, volume_fig, heights = c(0.7,0.2), nrows=2,
               shareX = TRUE, titleY = TRUE)
  final_fig <- final_fig %>% layout(
    title=list(text=paste0(eq_name,': ',dt,' - ',as.character(today_date)),
               font=list(size=22), y = 0.97),
    xaxis=list(type='date', tickformat = "%d %B <br>%Y",
               title=FALSE, tickfont=list(size=14)),
    yaxis=list(title="Price", titlefont=list(size=16),
               tickfont=list(size=14)),
    legend=list(orientation = 'h', x = 0.5, y = 0.93,
                xanchor = 'center', font = list(size=12),
                bgcolor = 'transparent')
  
  )
  #show
  final_fig
}
```
### Apple (AAPL) Graph
```{r}
data_viz1_func(aapl_df, 'AAPL')
```
### Disney (DIS) Graph
```{r}
data_viz1_func(dis_df, 'DIS')
```
### Netflix (NFLX) Graph
```{r}
data_viz1_func(nflx_df, 'NFLX')
```
### Roku (ROKU) Graph
```{r}
data_viz1_func(roku_df, 'ROKU')
```
### Spotify (SPOT) Graph
```{r}
data_viz1_func(spot_df, 'SPOT')
```
## Portfolio Analysis
Analysis of returns and equally weighted portfolio case study

Performance of selected equities independently
```{r}
#'AAPL', 'DIS', 'NFLX', 'ROKU', 'SPOT'
aapl_dret<-na.omit(dailyReturn(Ad(getSymbols.yahoo('AAPL',
                                        from=dt,
                                        periodicity='daily',
                                        auto.assign=F)), type='arithmetic'))
dis_dret<-na.omit(dailyReturn(Ad(getSymbols.yahoo('DIS',
                                        from=dt,
                                        periodicity='daily',
                                        auto.assign=F)), type='arithmetic'))
nflx_dret<-na.omit(dailyReturn(Ad(getSymbols.yahoo('NFLX',
                                        from=dt,
                                        periodicity='daily',
                                        auto.assign=F)), type='arithmetic'))
roku_dret<-na.omit(dailyReturn(Ad(getSymbols.yahoo('ROKU',
                                        from=dt,
                                        periodicity='daily',
                                        auto.assign=F)), type='arithmetic'))
spot_dret<-na.omit(dailyReturn(Ad(getSymbols.yahoo('SPOT',
                                        from=dt,
                                        periodicity='daily',
                                        auto.assign=F)), type='arithmetic'))
#renaming cols
colnames(aapl_dret)<-'AAPL.Ad.Returns'
colnames(dis_dret)<-'DIS.Ad.Returns'
colnames(nflx_dret)<-'NFLX.Ad.Returns'
colnames(roku_dret)<-'ROKU.Ad.Returns'
colnames(spot_dret)<-'SPOT.Ad.Returns'
#merging
dret_data<-cbind(aapl_dret,dis_dret,
                 nflx_dret,roku_dret,spot_dret)


table.AnnualizedReturns(dret_data, scale=252, Rf=0.015/252)
```
```{r fig.height=10}
#plotting performance
charts.PerformanceSummary(dret_data, main='Portfolio Performance',
                          Rf=0.015/252, plot.engine='default')
```

Equally weighted portfolio case study and analysis
```{r}
#eq weighted portfolio
portret_df<-Return.portfolio(dret_data,
                             weights=c(.20,.20,.20,.20,.20))
colnames(portret_df)<-'Porfolio.Eqw.Returns'

#performance benchmark
benchmarkPrices<-na.omit(dailyReturn(Ad(getSymbols.yahoo('^GSPC',
                                        from=dt,
                                        periodicity='daily',
                                        auto.assign=F)),
                                     type='arithmetic'))
colnames(benchmarkPrices)<-'Benchmark.SP500.Returns'

#merging portfolio and benchmark together
EqWPort.Benchmark_df<-merge(portret_df, benchmarkPrices)
#performance table 
table.AnnualizedReturns(EqWPort.Benchmark_df, scale=252, Rf=0.015/252)
```
```{r}

EqWPort.Benchmark_df<-data.frame(EqWPort.Benchmark_df)
EqWPort.Benchmark_df<-cbind(Date=rownames(EqWPort.Benchmark_df),
                            EqWPort.Benchmark_df)
rownames(EqWPort.Benchmark_df)<-1:nrow(EqWPort.Benchmark_df)

perf_fig<-EqWPort.Benchmark_df %>% plot_ly(x= ~Date,
                                      y=~Porfolio.Eqw.Returns,
                                      type='scatter',
                                      mode='lines',
                                      line = list(color='green',
                                             width=0.8),
                                 name='Portfolio', inherit = F,
                                 width=900, height=600)
perf_fig<-perf_fig %>% add_lines(x = ~Date,
                                 y = ~Benchmark.SP500.Returns,
                                 line = list(color='blue',
                                             width=0.8),
                                 name='S&P500', inherit = F)

#starting data
dt<-'2018-2-1'
#today's date
today_date<-Sys.Date()

#layout
perf_fig<- perf_fig %>% layout(
  title=list(text=paste0('Portfolio - S&P500',': ',dt,' - ',as.character(today_date)),
               font=list(size=22), y = 0.97),
  xaxis=list(type='date', tickformat = "%d %B <br>%Y",
               title=FALSE, tickfont=list(size=14)),
  yaxis=list(title="Returns", titlefont=list(size=16),
               tickfont=list(size=14))
  
)

perf_fig

```